Velocity Map Imaging Spectroscopy of C$_2$H$^-$ and C$_2$D$^-$: a benchmark study of vibronic coupling interactions

### 2022-06-24 Submission/Laws_C2H.tex
update resubmission

Chain growth of the C$_{2n}$H radicals occurs predominately through acetylene addition,~\cite{wil03}
\begin{equation}
\text{C}_{2n}\text{H} + \text{C}_2\text{H}_2 \rightarrow \text{C}_{2n+2}\text{H}+\text{H}_2.
\end{equation}
Conversely, the formation of anions in space is believed to be driven by radiative electron attachment, charge transfer, and dissociative electron attachment. Current astrochemical modelling of interstellar clouds, such as IRC+10216, typically underestimate the observed abundances of CH$_4^-$ ~\cite{mil17,cor13,her08}. Therefore, it has been proposed that ion-neutral reactions
\begin{equation}
\text{C}_{2n}\text{H}^- + \text{C}_2\text{H}_2 \rightarrow \text{C}_{2n+2}\text{H}^- + \text{H}_2.
\end{equation}
may be significant chain growth mechanisms that also needs to be included in astrochemical models~\cite{mil17,bas19}. Studies of the extraterrestrial planetary atmosphere of Saturn's moon Titan suggest that both C$_2$H and C$_2$H$^-$ play an important role in the atmospheric chemistry~\cite{dob16,vui09,des17,vri18}. Multiple reaction pathways involving the C$_2$H$^-$ have been proposed, including reactions with C$_2$H$_2$ and HCN.

@@

\subsection{Computational Details}
Quantum chemical computations were preformed using the CFOUR computational package~\cite{dev20}. The equation-of-motion ionised-potential coupled-cluster singles, doubles, and triples (EOM-IP-CCSDT) level of theory with an atomic natural orbital basis set of quadruple-zeta quality (ANO2) was used on a closed-shell anionic reference to perform geometry optimisations and frequency calculations (including 1h + 2h1p + 3h2p excitations~\cite{mat16}). EOM is a highly accurate and robust framework that provides access to different types of target electronic states, including ionised states~\cite{gul21b,and22,bar07}. The linear diabatic coupling constants were calculated analytically at the EOM-IP-CCSD/ANO2 level.

@@

\subsection{Coupling Calculations}
In order to guide spectral assignment of C$_2$H and future astronomical searches for other C$_n$H radicals, transition intensities are also needed. However, due to the strong vibronic coupling interactions, transition intensities can not be obtained via simple Franck-Condon calculations based on quantum chemistry methods. To account for these interactions, the photoelectron spectrum of the C$_2$H$^-$ anion is simulated using a quasidiabatic Hamiltonian of the type introduced by Koeppel, Domcke and Cederbaum (KDC).~\cite{kou84,dom81} In this approach, the Hamiltonian is represented in a basis of quasidiabatic (slowly varying) electronic  states for which the kinetic energy operator can be assumed diagonal.~\cite{pac93} For C$_2$H, the KDC Hamiltonian comprises three states - the two components of the $^2\Pi$ state and the ground $^2\Sigma^+$ state - and is then projected onto a vibrational basis, usually chosen as a direct product of harmonic oscillators. Diagonalization of the corresponding matrix yields the molecular states (which are given in terms of a Born-Huang expansion), and the squared projections of the corresponding eigenvectors onto the ground state of the anion yield the relative intensities. The latter is true only if the photodetachment cross sections for the $^2\Sigma^+$ and $^2\Pi$ states are assumed equal, but different cross sections of the two states can be incorporated by scaling the intensities of states according to their (vibronic) symmetry.~\cite{sta11}

@@

When the potential in Eq.~(\ref{eq:calc1}) is diagonalized, the adiabatic states that are used for its parametrization are precisely recovered through terms second order in displacement. The parametrization of the potential in this work was completed using the CFOUR computational package~\cite{dev20} and the quasidiabatic ansatz of Ichino~\emph{et al.}~\cite{ich09} Briefly,the EOM procedure is used to operationally define quasidiabatic states (those that relax according to a well-behaved reference state wavefunction, which is that of the anion level) and the coupling constants are then evaluated as the first derivative of the off-diagonal elements of the electronic Hamiltonian in the basis defined by this representation. Vertical excitation energies ($\Delta_0$), and linear diabatic force and coupling constants between the electronic states of interest were calculated analytically using the highly accurate EOM-IP-CCSDT/ANO2 procedure. The interstate coupling constants ($\lambda$) were calculated analytically at the EOM-IP-CCSD/ANO2 level. All calculated values used to parametrize the KDC potential in Eq.~(\ref{eq:calc1}) are presented in Table~\ref{tab:1}.

@@

\subsection{Simulated Spectra}
The above method was employed to simulate the photoelectron spectrum of C$_2$H$^-$, with the calculated transitions shown in Figure~\ref{fig:3}(a) alongside the experimental data at 355~nm. Photoelectron spectra are simulated using the xsim package of CFOUR~\cite{dev20} and the model Hamiltonian generated above. The xsim module projects the Hamiltonian (Eq.~\ref{eq:calc1}) onto a vibrational basis, which is then diagonalised using Lanczos algorithm to calculate transition energies and intensities that map to the measured photoelectron spectrum. In this simulation the transition moments for the two ionisation processes are assumed to be equal.   
On the $\tilde{X} ^2\Sigma^+$ surface, below 3,600~cm$^{-1}$, there is excellent agreement in both the transition positions and intensities between the simulated and experimental spectra. This includes the HT coupled (2$^{n+1}$) transitions with $\Pi$ symmetry, which would normally be missing from a simulation using the standard \emph{ab-initio} approaches.

@@

From Eq.~(\ref{eq:beta-sp}) it can be seen that detachment from a pure $s$ orbital ($\gamma_p=0$) will have a positive anisotropy ($\beta = +2$), whereas detachment from a pure $p$ orbital ($\gamma_p=1$) will have a negative anisotropy for electron kinetic energies $\epsilon < 2/A_1$. Therefore, measuring the anisotropy can help determine the electronic character of each individual transition, which may be compared to the calculated symmetries in Figure~\ref{fig:3}. For each prominent transition in the photoelectron spectrum of C$_2$H$^-$ in Figure~\ref{fig:1} the corresponding anisotropy parameter may be calculated by fitting Eq.~(\ref{eq:beta1}) to a plot of the integrated radial intensity (across the peak) versus angle, as (for a single quadrant of the electron image) the intensity variation is linear in $P_2(\cos\theta)$ with a slope equal to $\beta\times$intercept. This procedure was applied to all of the photoelectron spectra measured in this work, with the energy dependent anisotropy parameters presented in Figure~\ref{fig:5}(a).

\begin{figure}[th!]
	\includegraphics[width=0.8\textwidth]{figures/PAD}
	\caption{(a) Photoelectron anisotropy parameters, measured for each resolved C$_2$H$^-$ transition, across a range of detachment wavelengths. Allowed ground state transitions $\tilde{X}^2\Sigma^+$ are shown in orange, Herzberg-Teller coupled transitions are shown in purple, and excited state transitions $\tilde{A} ^2\Pi$ are shown in blue. Anisotropy curves for a mixed-$sp$ model (Eq.~\ref{eq:beta-sp}) are shown for $\gamma_p=0.1$ and $\gamma_p=0.9$. Anisotropy curves from Dyson orbital calculations for the $\tilde{X}^2\Sigma^+$ and $\tilde{A} ^2\Pi$ transitions are shown in blue and orange respectively. (b) Dyson orbital representation of the $\tilde{X}^1\Sigma^+\rightarrow\tilde{X}^2\Sigma^+$ transition. (c) Dyson orbital representation of the $\tilde{X}^1\Sigma^+\rightarrow\tilde{A} ^2\Pi$ transition.}
	\label{fig:5}
\end{figure}

In Figure~\ref{fig:5}(a) allowed ground state transitions ($\tilde{X}^2\Sigma^+$) are shown in blue and have a positive anisotropy, as expected for detachment from a $s-$like orbital. Conversely, excited state transitions ($\tilde{A} ^2\Pi$) shown in orange have a negative anisotropy. However, the HT coupled transitions on the $\tilde{X} ^2\Sigma^+$ surface also have negative anisotropies, due to their $\Pi$ vibronic symmetry. Therefore, the sign $(+/-)$ of $\beta$ can be used to assign each accessed vibronic level to either the $\Sigma$ or $\Pi$ vibronic symmetry respectively. This is particularly useful around the $\tilde{A} ^2\Pi$ origin, where the two states overlap. The mixed $sp$ model from Eq.~\ref{eq:beta-sp} is fitted to the experimental data in Figure~\ref{fig:5}(a) with $\gamma_p=0.1$ and $\gamma_p=0.9$ for the ground and excited state detachment respectively. For detachment to the $^2\Pi$ state this produces a Hanstorp coefficient of $A_1=0.66(4)~$eV$^{-1}$.

The photoelectron angular distribution may also be examined through the construction of Dyson orbitals, which provide a direct link between \emph{ab-initio} calculations and experimental anisotropy parameters. Q-Chem software~\cite{sha15} may be used to construct Dyson orbitals $\phi_d$ that represent the overlap between the initial $\phi_i^{(n)}$ and final $\phi_f^{(n-1)}$ states,
\begin{equation}
\phi_d = \sqrt{N}\int\phi_i^{(n)}(1,\dots,n)\phi_f^{(n-1)}(2,\dots,n)dn
\end{equation}
By representing the detached electron as a plane wave, $\psi_k=(2\pi)^{(-3/2)}e^{ik\cdot r}$ and assuming strong orthogonality between $\phi_d$, $\psi_k$, and $\phi_f^{(n-1)}$ the transition dipole moment may then be rewritten as
\begin{equation}
D_k \propto \langle \phi_d | e\cdot r | \psi_k\rangle.
\label{eq:Dyson}
\end{equation}
The Dyson orbital representation of the C$_2$H$^-$ $\tilde{X}^1\Sigma^+\rightarrow\tilde{X}^2\Sigma^+$ transition, calculated at the EOM-CCSD/aug-cc-pVTZ level, is shown in Figure~\ref{fig:5}(b). The corresponding anisotropy curve was calculated using ezDyson software~\cite{goz22}, and is shown in blue in Figure~\ref{fig:5}(a) alongside the experimental data. Figure~\ref{fig:5} shows that above threshold there is excellent agreement between the experimental anisotropies, the mixed $sp$ model (Eq.~\ref{eq:beta-sp}), and the calculated anisotropies (Eq.~\ref{eq:Dyson}). The cylindrical symmetry of the molecule introduces some $p$ character into the predominantly $s-$like Dyson orbital (Fig.~\ref{fig:5}(b)) which becomes significant near threshold due to the centrifugal detachment barrier. This makes the near threshold anisotropy behaviour sensitive to the exact amount of $p$ orbital character included in the orbital, an effect that has also been observed in NO$_2^-$ ~\cite{law19} and the isoelectronic CN$^-$ ~\cite{har21}. The Dyson orbital for the $\tilde{X}^1\Sigma^+\rightarrow\tilde{A} ^2\Pi$ transition was also calculated at the EOM-CCSD/aug-cc-pVTZ level, and is shown in Figure~\ref{fig:5}(c). Again the calculated anisotropy curve (shown in orange in Fig.~\ref{fig:5}(a)) appears a good match to the $sp$ model (Eq.~\ref{eq:beta-sp}) and the experimental data, however it overestimates the amount of $p$ orbital character.

>>>>

Chain growth of the C$_{2n}$H radicals occurs predominately through acetylene addition,~\cite{wil03}
\begin{equation}
\text{C}_{2n}\text{H} + \text{C}_2\text{H}_2 \rightarrow \text{C}_{2n+2}\text{H}+\text{H}_2.
\end{equation}
Conversely, the formation of anions in space is believed to be driven by radiative electron attachment, charge transfer, and dissociative electron attachment. Current astrochemical modelling of interstellar clouds, such as IRC+10216, typically underestimate the observed abundances of CH$_4^-$~\cite{mil17,cor13,her08}. Therefore, it has been proposed that ion-neutral reactions
\begin{equation}
\text{C}_{2n}\text{H}^- + \text{C}_2\text{H}_2 \rightarrow \text{C}_{2n+2}\text{H}^- + \text{H}_2.
\end{equation}
may be significant chain growth mechanisms that also needs to be included in astrochemical models~\cite{mil17,bas19}. Studies of the extraterrestrial planetary atmosphere of Saturn's moon Titan suggest that both C$_2$H and C$_2$H$^-$ play an important role in the atmospheric chemistry~\cite{dob16,vui09,des17,vri18}. Multiple reaction pathways involving the C$_2$H$^-$ have been proposed, including reactions with C$_2$H$_2$ and HCN.

@@

\subsection{Computational Details}
Quantum chemical computations were preformed using the CFOUR computational package~\cite{dev20}. The EOM-CCSDT/ANO2 level of theory was used to perform geometry optimisations and frequency calculations. The linear diabatic coupling constants were calculated analytically at the EOM-CCSD/ANO2 level.

@@

\subsection{Coupling Calculations}
In order to guide spectral assignment of C$_2$H and future astronomical searches for other C$_n$H radicals, transition intensities are also needed. However, due to the strong vibronic coupling interactions, transition intensities can not be obtained via simple Franck-Condon calculations based on quantum chemistry methods. To account for these interactions, the photoelectron spectrum of the C$_2$H$^-$ anion is simulated using a quasidiabatic Hamiltonian of the type advocated by Koeppel, Domcke and Cederbaum (KDC).~\cite{kou84,dom81} In this approach, the Hamiltonian is represented in a basis of quasidiabatic (slowly varying) electronic  states for which the kinetic energy operator can be assumed diagonal.~\cite{pac93} For C$_2$H, the KDC Hamiltonian comprises three states - the two components of the $^2\Pi$ state and the ground $^2\Sigma^+$ state - and is then projected onto a vibrational basis, usually chosen as a direct product of harmonic oscillators. Diagonalization of the corresponding matrix yields the molecular states (which are given in terms of a Born-Huang expansion), and the squared projections of the corresponding eigenvectors onto the ground state of the anion yield the relative intensities. The latter is true only if the photodetachment cross sections for the $^2\Sigma^+$ and $^2\Pi$ states are assumed equal, but different cross sections of the two states can be incorporated by scaling the intensities of states according to their (vibronic) symmetry.~\cite{sta11}

@@

When the potential in Eq.~(\ref{eq:calc1}) is diagonalized, the adiabatic states that are used for its parametrization are precisely recovered through terms second order in displacement. The linear diabatic coupling constants between the electronic states of interest were calculated analytically at the EOM-CCSD/ANO2 level of theory, using the CFOUR computational package~\cite{dev20} and the quasidiabatic ansatz of Ichino~\emph{et al.}~\cite{ich09} Briefly, the EOM procedure is used to operationally define quasidiabatic states (those that relax according to a well-behaved reference state wavefunction, which is that of the anion level) and the coupling constants are then evaluated as the first derivative of the off-diagonal elements of the electronic Hamiltonian in the basis defined by this representation. The diabatic force and coupling constants calculated to parametrize the KDC potential in Eq.~(\ref{eq:calc1}) were calculated at the CCSDT/ANO2 level of theory, and are presented in Table~\ref{tab:1}.

@@

\subsection{Simulated Spectra}
The above method was employed to simulate the photoelectron spectrum of C$_2$H$^-$, with the calculated transitions shown in Figure~\ref{fig:3}(a) alongside the experimental data at 355~nm. Photoelectron spectra are simulated using the xsim package of CFOUR and the model Hamiltonian generated above. The Hamiltonian is diagonalised using the Lanczos algorithm, to calculate transition energies and intensities that map to the measured photoelectron spectrum.  
On the $\tilde{X} ^2\Sigma^+$ surface, below 3,600~cm$^{-1}$, there is excellent agreement in both the transition positions and intensities between the simulated and experimental spectra. This includes the HT coupled (2$^{n+1}$) transitions with $\Pi$ symmetry, which would normally be missing from a simulation using the standard \emph{ab-initio} approaches.

@@

From Eq.~(\ref{eq:beta-sp}) it can be seen that detachment from a pure $s$ orbital ($\gamma_p=0$) will have a positive anisotropy ($\beta = +2$), whereas detachment from a pure $p$ orbital ($\gamma_p=1$) will have a negative anisotropy for electron kinetic energies $\epsilon < 2/A_1$. Therefore, measuring the anisotropy can help determine the electronic character of each individual transition, which may be compared to the calculated symmetries in Figure~\ref{fig:3}. Anisotropy parameters were measured over a range of detachment wavelengths for prominent transitions in the C$_2$H$^-$ photoelectron spectra, and are presented in Figure~\ref{fig:5}. Fitting Eq.~(\ref{eq:beta-sp}) to the anisotropy parameters from $^2\Pi$ state detachment, with $\gamma_p = 0.9$ produces a Hanstorp coefficient of $A_1=0.66(4)~$eV$^{-1}$.

\begin{figure}[th!]
	\includegraphics[width=0.5\textwidth]{figures/Fig5}
	\caption{Photoelectron anisotropy parameters, measured for each resolved C$_2$H$^-$ transition, across a range of detachment wavelengths. Allowed ground state transitions $\tilde{X}^2\Sigma^+$ are shown in orange, Herzberg-Teller coupled transitions are shown in purple, and excited state transitions $\tilde{A} ^2\Pi$ are shown in blue. Anisotropy curves for a mixed-$sp$ model (Eq.~\ref{eq:beta-sp}) are shown for $\gamma_p=0.1$ and $\gamma_p=0.9$.}
	\label{fig:5}
\end{figure}

The sign $(+/-)$ of $\beta$ can be used to assign each accessed vibronic level to either the $^2\Sigma^+$ or $^2\Pi$ vibronic symmetry respectively. This is particularly useful around the $\tilde{A} ^2\Pi$ origin, where the two states overlap. It is important to note that the HT coupled transitions on the $\tilde{X} ^2\Sigma^+$ surface have negative anisotropies and $\Pi$ symmetry.

### 2022-06-24 Submission/suppInfo.tex
update resubmission

\documentclass[journal=jacsat,manuscript=suppinfo]{achemso}
%\usepackage{scicite}
\usepackage[sort&compress, numbers]{natbib}
\usepackage{times}
\usepackage{amssymb}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{upgreek}
\usepackage{gensymb}
%\usepackage[colorlinks]{hyperref}
%\newcommand{\hah}[1]{\textcolor{magenta}{#1}}
\newcommand{\tws}[1]{\textcolor{red}{#1}}
\usepackage[version=4]{mhchem}
\usepackage{amsmath,amsfonts,amssymb,dcolumn,lscape,alltt,graphicx,chemarr}
\usepackage[english]{babel}
\SectionNumbersOn
\usepackage{bm}
\usepackage[T1]{fontenc}
\usepackage{chemstyle}
% NB added command for in line cite
\newcommand{\onlinecite}[1]{\hspace{-1 ex} \nocite{#1}\citenum{#1}}
% 2 column equations
%\usepackage{widetext, widetable}
%
\author{Benjamin~A.~Laws}
\email{b.laws@unsw.edu.au}
\affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
\alsoaffiliation{Research School of Physics, The Australian
	National University, Canberra ACT 2601, Australia}
\author{Zachariah~D.~Levey} 
\affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
\author{Andrei M. Sanov}
\affiliation{Department of Chemistry and Biochemistry, The University of Arizona, Tucson, Arizona 85721, United States}
\author{John F. Stanton}
\affiliation{Department of Chemistry, University of Florida, Gainesville, Florida 32611, United States}
\author{Timothy~W.~Schmidt} 
\affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
\author{Stephen~T.~Gibson}
\affiliation{Research School of Physics, The Australian
	National University, Canberra ACT 2601, Australia}
\title{Velocity Map Imaging Spectroscopy of C$_2$H$^-$ and C$_2$D$^-$: a benchmark study of vibronic coupling interactions}
\abbreviations{PES,PAD,EA,eKE,FWHM,VMI}
%\DeclareUnicodeCharacter{2192}{-}

@@

\section{C$_2$H$^-$ Spectral Assignments}
Spectral assignments for all peaks resolved in the photoelectron spectra of C$_2$H$^-$ from this work are presented in Table~\ref{tab:1}. Peaks are labelled with respect to the photoelectron spectrum of C$_2$H$^-$ at 300~nm in Figure~\ref{fig:1}. The experimental binding energy of each transition is given, alongside the anisotropy ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}. Assignments are given as $\tilde{X}(v_1,v_2,v_3)\tilde{A}(v_1,v_2,v_3)$ where superscripts represent hot-band transitions.

\begin{figure}[th!]
	\includegraphics[width=0.6\textwidth]{figures/FigS1.pdf}
	\caption{Photoelectron spectrum of C$_2$H$^-$ at 300~nm, showing the labelling of peaks used in this work.}
	\label{fig:1}
\end{figure}

@@

\section{C$_2$D$^-$ Spectral Assignments}
Spectral assignments for all peaks resolved in C$_2$D$^-$ from this work are presented in Table~\ref{tab:2}. Peaks are labelled with respect to the photoelectron spectrum of C$_2$D$^-$ at 355~nm in Figure~\ref{fig:2}. The experimental binding energy of each transition is given, alongside the anisotropy ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}.

\begin{figure}[th!]
	\includegraphics[width=0.6\textwidth]{figures/FigS2.pdf}
	\caption{Photoelectron spectrum of C$_2$D$^-$ at 266~nm, showing the labelling of peaks used in this work.}
	\label{fig:2}
\end{figure}

>>>>

\documentclass[journal=jacsat,manuscript=suppinfo]{achemso}
%\usepackage{scicite}
\usepackage[sort&compress, numbers]{natbib}
\usepackage{times}
\usepackage{amssymb}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{upgreek}
\usepackage{gensymb}
%\usepackage[colorlinks]{hyperref}
%\newcommand{\hah}[1]{\textcolor{magenta}{#1}}
\newcommand{\tws}[1]{\textcolor{red}{#1}}
\usepackage[version=4]{mhchem}
\usepackage{amsmath,amsfonts,amssymb,dcolumn,lscape,alltt,graphicx,chemarr}
\usepackage[english]{babel}
\SectionNumbersOn
\usepackage{bm}
\usepackage[T1]{fontenc}
\usepackage{chemstyle}
% NB added command for in line cite
\newcommand{\onlinecite}[1]{\hspace{-1 ex} \nocite{#1}\citenum{#1}}
% 2 column equations
%\usepackage{widetext, widetable}
%
\author{Benjamin~A.~Laws}
\email{b.laws@unsw.edu.au}
\affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
\alsoaffiliation{Research School of Physics, The Australian
	National University, Canberra ACT 2601, Australia}
\author{Zachariah~D.~Levey} 
\affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
\author{Andrei Sanov}
\affiliation{Department of Chemistry and Biochemistry, The University of Arizona, Tucson, Arizona 85721, United States}
\author{John F. Stanton}
\affiliation{Department of Chemistry, University of Florida, Gainesville, Florida 32611, United States}
\author{Timothy~W.~Schmidt} 
\affiliation{School of Chemistry, University of New South Wales, Sydney NSW 2052, Australia}
\author{Stephen~T.~Gibson}
\affiliation{Research School of Physics, The Australian
	National University, Canberra ACT 2601, Australia}
\title{Velocity Map Imaging Spectroscopy of C$_2$H$^-$ and C$_2$D$^-$: a benchmark study of vibronic coupling interactions}
\abbreviations{PES,PAD,EA,eKE,FWHM,VMI}
%\DeclareUnicodeCharacter{2192}{-}

@@

\section{C$_2$H$^-$ Spectral Assignments}
Spectral assignments for all peaks resolved in the photoelectron spectra of C$_2$H$^-$ from this work are presented in Table~\ref{tab:1}. Peaks are labelled with respect to the photoelectron spectrum of C$_2$H$^-$ at 300~nm in Figure~\ref{fig:1}. The experimental binding energy of each transition is given, alongside the anisotropy parameter sign ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}. Assignments are given as $\tilde{X}(v_1,v_2,v_3)\tilde{A}(v_1,v_2,v_3)$ where any superscripts represent hot-band transitions.

\begin{figure}[th!]
	\includegraphics[width=0.6\textwidth]{figures/FigS1}
	\caption{Photoelectron spectrum of C$_2$H$^-$ at 300~nm, showing the alphabetic labelling of peaks used in this work.}
	\label{fig:1}
\end{figure}

@@

\section{C$_2$D$^-$ Spectral Assignments}
Spectral assignments for all peaks resolved in C$_2$D$^-$ from this work are presented in Table~\ref{tab:2}. Peaks are labelled with respect to the photoelectron spectrum of C$_2$D$^-$ at 355~nm in Figure~\ref{fig:2}. The experimental binding energy of each transition is given, alongside the anisotropy parameter sign ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}.

\begin{figure}[th!]
	\includegraphics[width=0.6\textwidth]{figures/FigS2}
	\caption{Photoelectron spectrum of C$_2$D$^-$ at 266~nm, showing the alphabetic labelling of peaks used in this work.}
	\label{fig:2}
\end{figure}

### 2022-06-24 suppInfo.tex
update resubmission

\section{C$_2$H$^-$ Spectral Assignments}
Spectral assignments for all peaks resolved in the photoelectron spectra of C$_2$H$^-$ from this work are presented in Table~\ref{tab:1}. Peaks are labelled with respect to the photoelectron spectrum of C$_2$H$^-$ at 300~nm in Figure~\ref{fig:1}. The experimental binding energy of each transition is given, alongside the anisotropy ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}. Assignments are given as $\tilde{X}(v_1,v_2,v_3)\tilde{A}(v_1,v_2,v_3)$ where superscripts represent hot-band transitions.

\begin{figure}[th!]
	\includegraphics[width=0.6\textwidth]{figures/FigS1.pdf}
	\caption{Photoelectron spectrum of C$_2$H$^-$ at 300~nm, showing the labelling of peaks used in this work.}
	\label{fig:1}
\end{figure}

@@

\section{C$_2$D$^-$ Spectral Assignments}
Spectral assignments for all peaks resolved in C$_2$D$^-$ from this work are presented in Table~\ref{tab:2}. Peaks are labelled with respect to the photoelectron spectrum of C$_2$D$^-$ at 355~nm in Figure~\ref{fig:2}. The experimental binding energy of each transition is given, alongside the anisotropy ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}.

\begin{figure}[th!]
	\includegraphics[width=0.6\textwidth]{figures/FigS2.pdf}
	\caption{Photoelectron spectrum of C$_2$D$^-$ at 266~nm, showing the labelling of peaks used in this work.}
	\label{fig:2}
\end{figure}

>>>>

\section{C$_2$H$^-$ Spectral Assignments}
Spectral assignments for all peaks resolved in the photoelectron spectra of C$_2$H$^-$ from this work are presented in Table~\ref{tab:1}. Peaks are labelled with respect to the photoelectron spectrum of C$_2$H$^-$ at 300~nm in Figure~\ref{fig:1}. The experimental binding energy of each transition is given, alongside the anisotropy parameter sign ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}. Assignments are given as $\tilde{X}(v_1,v_2,v_3)\tilde{A}(v_1,v_2,v_3)$ where any superscripts represent hot-band transitions.

\begin{figure}[th!]
	\includegraphics[width=0.6\textwidth]{figures/FigS1.pdf}
	\caption{Photoelectron spectrum of C$_2$H$^-$ at 300~nm, showing the alphabetic labelling of peaks used in this work.}
	\label{fig:1}
\end{figure}

@@

\section{C$_2$D$^-$ Spectral Assignments}
Spectral assignments for all peaks resolved in C$_2$D$^-$ from this work are presented in Table~\ref{tab:2}. Peaks are labelled with respect to the photoelectron spectrum of C$_2$D$^-$ at 355~nm in Figure~\ref{fig:2}. The experimental binding energy of each transition is given, alongside the anisotropy parameter sign ($+/-$), the corresponding vibronic symmetry, and the calculated energy from Ref.~\onlinecite{tar03}.

\begin{figure}[th!]
	\includegraphics[width=0.6\textwidth]{figures/FigS2.pdf}
	\caption{Photoelectron spectrum of C$_2$D$^-$ at 266~nm, showing the alphabetic labelling of peaks used in this work.}
	\label{fig:2}
\end{figure}
